\begin{document}
\noindent \textbf{Sachin Thomas} \\
2942 Wessels Dr \\
Troy, MI 48085 \\
(248) 918-8263 \\
\vspace{8pt}
\noindent \textbf{2025-05-15} \\
\vspace{4pt}
\noindent \textbf{Ramp}
\newline

\noindent Dear Ramp Team, \\

\noindent I'm excited to apply for the Front-End Engineer position at Ramp. With over 8 years of experience building modern, high-performance web applications, I'm eager to contribute to Ramp's mission of transforming financial operations for businesses at scale.
\newline\newline
\noindent At Latcha \& Associates, I've developed and led front-end initiatives using React, Angular, and TypeScript, optimizing user experience and system performance for large-scale platforms. My work on marketing automation and real-time dashboards has helped drive both business value and customer satisfaction—experiences that strongly align with Ramp's emphasis on impactful, scalable solutions. I'm particularly enthusiastic about your use of TypeScript, React, and Vite, and share your dedication to shipping polished, user-centered products.
\newline\newline
\noindent I admire Ramp's rapid growth, innovative culture, and commitment to excellence. The opportunity to collaborate on high-impact projects and contribute to a forward-thinking engineering team resonates deeply with my own values of velocity, humility, and continuous improvement.
\newline\newline
Thank you for considering my application. I'd welcome the chance to connect and explore how I can help further Ramp's vision and engineering excellence.
\newline\newline
\noindent Best regards,\\
\noindent Sachin Thomas

% \vspace{24pt}
% \hrule
% \vspace{10pt}
% \small \color{rulered} {\textbf{Note} This cover letter is not intended to use as is.}